Binary companions of red giant stars with APOGEE: \\ catalog and companions that survive the common envelope

### 2018-02-01 paper/1-catalog/twoface-catalog.tex
data

@@

From the \apogee\ \DR\ data products (the \texttt{allStar} and \texttt{allVisit}
files), we select all stars with $\geq 3$ visits that each pass a set of quality
cuts.
For each visit, we require that the following bits are not set in the
\texttt{STARFLAGS} bitmask: \texttt{TODO}.
For each star, we require that the following bits are not set in the
\texttt{ASPCAPFLAGS} bitmask: \texttt{TODO}.
After these cuts, and the requirement of $\geq 3$ visits for a given star, we
are left with \todo{XX} visits for \todo{XX} unique stars (unique
\texttt{APOGEE\_ID}).
\todo{add numpy code for exact filter?}

>>>>

\graphicspath{{figures/}}

@@

We use the primary data products from \apogee\ \DR\ (i.e. the \texttt{allStar}
and \texttt{allVisit} files) which contain 258475 unique source IDs
(\texttt{APOGEE\_ID}) and 1054381 unique visits.
We select all stars with $\geq 3$ visits that each pass a set of quality cuts,
described below.
For each visit, we require that the visit velocity uncertainty is $< 100~\kms$
(\texttt{VRELERR}) and the following bits are not set in the \texttt{STARFLAGS}
bitmask: \texttt{PERSIST\_HIGH}, \texttt{PERSIST\_JUMP\_POS},
\texttt{PERSIST\_JUMP\_NEG}, \texttt{VERY\_BRIGHT\_NEIGHBOR}, \texttt{LOW\_SNR}.
For each star, we require that $0 < \log g < 3.5$ and the following bits are not
set in the \texttt{ASPCAPFLAGS} bitmask: \texttt{STAR\_BAD}.
After these cuts, and the requirement of $\geq 3$ visits for a given star, we
are left with \todo{XX} visits for \todo{XX} unique stars (unique
\texttt{APOGEE\_ID}).
\todo{add numpy code for exact filter?}
\figurename~\ref{fig:nvisits} shows the number of stars in several bins of
number of visits that pass the above quality cuts: \todo{XX}\% of the stars in
\DR\ have $< 8$ visits.

% Notebook: "Numbers after cuts"
\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{nvisits.pdf}
\end{center}
\caption{%
TODO: \label{fig:nvisits}
}
\end{figure}
